Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 draft.tex
blank author list and funding infor in Ack

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig
\usepackage{verbatim}
\usepackage{soul}
\usepackage{xcolor}
\newcommand{\TODO}[1]{\hl{TODO: #1}}
\newcommand{\NOTE}[1]{\hl {NOTE: #1}}
\newcommand{\changed}[1]{\textcolor{red}{#1}}

@@

%\author{
%
%\IEEEauthorblockN{Xu Yang\IEEEauthorrefmark{1}, John Jenkins\IEEEauthorrefmark{2}, Misbah Mubarak\IEEEauthorrefmark{2}, Robert B. Ross\IEEEauthorrefmark{2}, Zhiling Lan\IEEEauthorrefmark{1}}
%
%\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science,
%Illinois Institute of Technology,
%Chicago, Illinois, USA 60616\\
%\{xyang56\}@hawk.iit.edu, lan@iit.edu}
%
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Mathematics and Computer Science Division, Argonne National Laboratory,
%Argonne, IL, USA 60439\\
%\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}
%}

@@

%The work at Illinois Institute of Technology is supported in part by U.S. National Science Foundation grants CNS-1320125 and CCF-1422009. This work is also supported by the U.S. Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract DE-AC02-06CH11357.

This work is supported in part by U.S. National Science Foundation and U.S. Department of Energy, Office of Science.

@@

%\begin{framed}
% The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").  Argonne, a U.S. Department of Energy Office of Science laboratory, is operated under Contract No. DE-AC02-06CH11357.  The U.S. Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
%\end{framed}

>>>>

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

%*******to add TODO and NOTE***********
\usepackage{verbatim}
\usepackage{soul}
\usepackage{xcolor}
\newcommand{\TODO}[1]{\hl{TODO: #1}}
\newcommand{\NOTE}[1]{\hl {NOTE: #1}}
\newcommand{\changed}[1]{\textcolor{red}{#1}}
%*******to blank author for blind review*********
\sethlcolor{black}
\makeatletter
\newif\if@blind
\@blindtrue %use \@blindfalse on final version
\if@blind \sethlcolor{black}\else
   \let\hl\relax
\fi

@@

\author{

\IEEEauthorblockN{\hl{Xu Yang}\IEEEauthorrefmark{1}, \hl{John Jenkins}\IEEEauthorrefmark{2}, \hl{Misbah Mubarak}\IEEEauthorrefmark{2}, \hl{Robert B. Ross}\IEEEauthorrefmark{2}, \hl{Zhiling Lan}\IEEEauthorrefmark{1}}

\IEEEauthorblockA{\IEEEauthorrefmark{1}\hl{Department of Computer Science,
Illinois Institute of Technology,
Chicago, Illinois, USA 60616}\\
\hl{\{xyang56\}@hawk.iit.edu, lan@iit.edu}}

\IEEEauthorblockA{\IEEEauthorrefmark{2}\hl{Mathematics and Computer Science Division, Argonne National Laboratory,
Argonne, IL, USA 60439}\\
\hl{\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}}

}

@@

The work at \hl{Illinois Institute of Technology} is supported in part by U.S. National Science Foundation grants \hl{CNS-1320125 and CCF-1422009}. This work is also supported by the U.S. Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract \hl{DE-AC02-06CH11357.}

%This work is supported in part by U.S. National Science Foundation and U.S. Department of Energy, Office of Science.

@@

\begin{framed}
The submitted manuscript has been created by \hl{ UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").  Argonne, a U.S. Department of Energy Office of Science laboratory, is operated under Contract No. DE-AC02-06CH11357. } The U.S. Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
\end{framed}
